\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Space Shooter}

\author{Team \#105, Space Shooter
		\\ Nishanth Raveendran, raveendn
		\\ Dananjay Prabaharan, prabahad
		\\ Hongzhao Tan, tanh10
}

\date{}

\begin{document}

\maketitle

\newpage

\section{Revision History}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Jan 22 & Raveendran, Nishanth & Initial Problem Statement Draft\\
Jan 22 & Prabaharan, Dananjay & Initial Problem Statement Draft\\
Jan 22 & Tan, Hongzhao & Initial Problem Statement Draft\\
\bottomrule
\end{tabularx}
\end{table}

\newpage
\section{Problem Statement}

\subsection{What problem are you trying to solve?}

In this modern age of gaming, there are many large scale complex games available on different platforms. Some of these games require lots of time investment to improve skills and progress in the game. This does not suffice for people looking for casual entertainment, who want games much like the simple arcade games from the 80’s. The game we are looking to improve is an old school arcade style game, like “Space Invaders”, that is easy to pick up and play. We plan on creating a better, more intuitive user interface so it is easier to use. We will also implement new features to make the game more interesting. These new features may include new enemy types, powerups, more mobility, and other possibilities. Overall, we are looking to improve “Space Shooter” to make it more user friendly and appealable to a more general audience. 


\subsection{Why is this an important problem?}

“Space Invaders” was a classic game that used to be played heavily by people of all ages in the 80’s. As PC, mobile and console games are quickly becoming a replacement for in-person arcades, the younger generation is missing out on classic games that used to be embraced in the past. In addition, games in today’s society have greatly increased in complexity and several gamers currently don’t have games that they could play casually. With the modern version of the game, Space Shooter, younger generations would now have a game to play casually that was enjoyed greatly in the past. The modern version would also incorporate several trends from today’s games such as power ups, new enemy types, and increased mobility, to create an addicting and fun environment for users to play in.

\subsection{What is the context of the problem you are solving?}

“Space Shooter” is a game that can be played on any PC with Windows or MacOS. The target market for Space Shooters are children and the older generation who have played the game in the past and want to nostalgically look back. Users can easily download the game for free online and play it locally on their PC with one-click.  The primary stakeholders of “Space Shooter” are the clients, developers, and testers. The clients are the end-users who play the game on their local PC while the developers and testers would be Team 105. Team 105’s role is committed to develop additional features for the game based on the old classic for modern day users to enjoy. This includes in-game powerups, increased mobility, and new enemy types. 

\end{document}